Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-11-26 paper_comparison/paper_comparison/paper_comparison.Rmd
update result text

<!-- Figure \ref{fig:power-poly-uniform} shows the estimated power of visual test on lineups with uniform distribution $X_{raw}$ against natural logarithm of the effect with comparison to the power of an exact test - F-test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing other departures from the model assumptions. In overall, the power of all four tests increases as the effect becomes larger. The power curve of F-test climbs aggressively from 25% to around 90% as $log_e(E)$ increases from 0 to 2, while others respond inactively to the change of effect and remain lower than 25% throughout the period, showing that as an exact test, the F-test is relatively more sensitive to the type of model defects that being considered. The power of visual test arises steadily and nearly linearly to around 90% as $log_e(E)$ increases from 2 to 5, suggesting that the effect starts to make noticeable impact on the degree of the presence of the designed visual features. Other two inappropriate conventional tests shows improvement at the same time but at a lower rate. This coincides the point made by @cook1982residuals mentioned in \ref{hypothesis-testing} that residual-based tests for a specific type of model defect are sensitive to other types of model defects. At $log_e(E) \approx 6$, the power curve of F-test reaches almost 100% followed by the visual test by a small margin. The power of Breusch--Pagan test and Shapiro--Wilk test reach around 75% and 30% respectively. -->

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with the $X_{raw}$ following a uniform distribution against the natural logarithm of the effect with comparison to the power of an exact test - F-test, and two other residual-based conventional tests commonly used in regression diagnostics but for testing heteroskedasticity and non-normality respectively. In overall, the power of all four teste eincreases as the effect becomes larger. The power curve of F-test climbs aggressively from 25% to around 90% as $log_e(E)$ increases from 0 to 2, while power of other tests respond inactively to the change of effect and remain lower than 25% throughout the period, showing that F-test is way more sensitive to the type of model defects that being considered. The power of visual test arises steadily to around 90% as $log_e(E)$ increases from 2 to 5, suggesting that the effect starts to make noticeable impact on the degree of the presence of the designed visual features. Other two inappropriate conventional tests shows improvement at the same time but at a lower rate. This coincides the point made by @cook1982residuals that residual-based tests for a specific type of model defect are sensitive to other types of model defects. At $log_e(E) \approx 6$, the power of both F-test and visual test reaches almost 100%. The power of Breusch--Pagan test and Shapiro--Wilk test reach around 75% and 30% respectively.

### 2022-11-26 paper_comparison/paper_comparison/paper_comparison.tex
update result text

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with the \(X_{raw}\)
following a uniform distribution against the natural logarithm of the
effect with comparison to the power of an exact test - F-test, and two
other residual-based conventional tests commonly used in regression
diagnostics but for testing heteroskedasticity and non-normality
respectively. In overall, the power of all four teste eincreases as the
effect becomes larger. The power curve of F-test climbs aggressively
from 25\% to around 90\% as \(log_e(E)\) increases from 0 to 2, while
power of other tests respond inactively to the change of effect and
remain lower than 25\% throughout the period, showing that F-test is way
more sensitive to the type of model defects that being considered. The
power of visual test arises steadily to around 90\% as \(log_e(E)\)
increases from 2 to 5, suggesting that the effect starts to make
noticeable impact on the degree of the presence of the designed visual
features. Other two inappropriate conventional tests shows improvement
at the same time but at a lower rate. This coincides the point made by
\citet{cook1982residuals} that residual-based tests for a specific type
of model defect are sensitive to other types of model defects. At
\(log_e(E) \approx 6\), the power of both F-test and visual test reaches
almost 100\%. The power of Breusch--Pagan test and Shapiro--Wilk test
reach around 75\% and 30\% respectively.
